### 2017-02-23 paper.tex
blah

% \setlength{\columnsep}{10mm}
% \setlength{\textwidth}4.0180mm}
% \setlength{\textheight}{250mm}
% \addtolength{\oddsidemargin}{-9mm}
% \addtolength{\topmargin}{-25mm}

@@

% *** Do not adjust lengths that control margins, column widths4.0 etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

@@

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=4.0.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex,
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation results for the network.}
%\label{fig_sim}
%\end{figure}

@@

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command,
% and the \label for the overall figure must come after \caption.
% \hfil is used as a separator to get equal spacing.
% Watch out that the combined width 4.0f all the subfigures on a
% line do not exceed the text width 4.0r a line break will occur.
%
%\begin{figure*}[!t]
%\centering
%\subfloat[Case I]{\includegraphics[width=4.0.5in]{box}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=4.0.5in]{box}%
%\label{fig_second_case}}
%\caption{Simulation results for the network.}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat[]), but instead will
%  reference/describe all of them (a), (b), etc., within the main caption.
% Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
% labels, the optional argument to \subfloat must be present. If a
% subcaption is not desired, just leave its contents blank,
% e.g., \subfloat[].

@@

\begin{figure}[!t]
\centering
\caption{Overview of network function}
\includegraphics[width=4.0in]{./figures/nfv_overview}
\label{fig:nfv_overview}
\end{figure}

@@

\begin{figure}[!t]
\centering
\includegraphics[width=4.0in]{./figures/deployment}
\caption{Service Deployment Model}
\label{fig:vcpe_deploy}
\end{figure}

@@

\begin{figure}[!t]
\centering
\includegraphics[width=4.0in]{./figures/vcpe_framework_overview}
\caption{Overview of vCPE framework}
\label{fig:vcpe_framework}
\end{figure}

@@

\subsubsection{QoS}
Quality of Service (QoS) are always used to control the traffic flows of a network
and prevent the traffic to exceed the network capacity and cause traffic congestion.
Therefore we implement the bandwidth 4.0anagement using meter
which is defined within OpenFlow protocol 1.3 to set the limitation of the bandwidth.4.0Beside achieving network functions virtualization with SDN technology,
we also make the network administrator manage and monitor a network more easily.
As a result, we can offer the user the best network quality in the limited network resource without traffic congestion.
In this paper, our QoS integrates with a flow classification engine
and offers the three ways of bandwidth 4.0anagement:
\begin{itemize}
\item For a specific host..
\item For a specific host.
\item For a specific application from a host or a domain.
\end{itemize}

\subsection{Application Identification}
Application identification is to identify each flow
as an application name to enable QoS management system to do bandwidth 4.0ontrol or distribution at application level.
A flow is defined by 5-tuple (source IP, source port, destination IP, destination port, and transport layer protocol).
Applications include desktop applications, native mobile applications, and web applications,
such as Facebook, Skype, YouTube, Instagram, Line and WeChat.
We use supervised machine learning and a method based on inspecting domain name service (DNS) responses to do flow classification.
After application identification system classifies a flow as an application name,
it sends the classification result to a server with database.
The server stores the classification result into database, and waits for query with 5-tuple from QoS management system.
The detail will be described in section \ref{sec:app_classification}.

@@

\begin{figure}[!t]
\centering
\includegraphics[width=4.0in]{./figures/multiple_table}
\caption{The flow table order of our vCPE service}
\label{fig:table-seq}
\end{figure}

@@

\subsection{NAT}
\begin{figure}[!t]
\centering
\includegraphics[width=4.0in]{./figures/nat_illustrate}
\caption{Illustration of NAT service}
\label{fig:nat_illustration}
\end{figure}
The NAT service could allow a lot of hosts to use one public IP address to connect the network.
In order to achieve this thing, SDN controller have to set the packet header filed.
Because the SDN switch would set the field, the first packet have to go to controller.
And controller would add the flow to SDN switch, after that the packet would not go to controller.
It can decrease the burdens of the controller.

@@

In order to gather per-session statistics information, 5-tuple rules are needed. This is why we don’t add rules  based on mac address.  The controller installs a pair of dummy rules for every connection, and then request the switch to get current flow statistics every second. In this way, we can get the real-time bandwidth 4.0tatistics of each connection by just subtracting the byte count from byte count of last second.

\section{Application Identifier method} \label{sec:app_classification}
In order to let QoS management system be able to control or distribute bandwidth 4.0t application level, we designed and implemented an application identification system (also called flow classification system) to judge each flow is established by what application. In other words, the system can classify each flow as an application name in real time, rather than a rough category or a transport layer protocol.
We use supervised machine learning (ML) and a method based on inspecting domain name service (DNS) responses to do flow classification. Except for DNS responses, the system only analyzes transport layer information of packets without inspecting their payload

@@

\begin{figure}[!t]
\centering
\includegraphics[width=4.0in]{./figures/classification_training}
\caption{Architecture of our application identification system in training phase}
\label{fig:classifcation_training}
\end{figure}

\begin{figure}[!t]
\centering
\includegraphics[width=4.0in]{./figures/classification_classifying}
\caption{Architecture of our application identification system in classifying phase}
\label{fig:classifcation_classifying}
\end{figure}

@@

\begin{figure}[!t]
\centering
\includegraphics[width=4.0in]{./figures/nat_evaluation}
\caption{Multiple Table Performance Evaluation Scenario}
\label{fig:nat_evaluation}
\end{figure}

\begin{figure}[!t]
\centering
\includegraphics[width=4.0in]{./figures/nat_evaluation_result}
\caption{Result of Multiple Table Performance Evaluation}
\label{fig:nat_evaluation_result}
\end{figure}

The single table framework implementation is easier than multiple table framework, but the multiple table framework is more flexible. To verify the efficacy of multiple table vCPE framework, this experiment use the NAT service to compare the throughput between single table vCPE and multiple table vCPE.
To begin with, an overview of the experiment environment illustrated in Fig. \ref{fig:nat_evaluation}.  In this experiment, the controller is Ryu SDN controller, and run on the Dell PowerEdge R630 Rack Server. The SDN switch employ Pica8 P-3290 switch. We used the tool that iPerf2.0 could generate the network traffic. The iPerf server would be set a public IP address. And iPerf client connect to the SDN switch that the controller would execute the NAT service on the single and multiple table vCPE framework.
We use the iPerf  to generate the UDP packets and send to server from client, and set the fixed value to bandwidth 4.0t 100Mbps. These experiments would use diffrent payload sizes to inspect their performances.
As shown in Fig. \ref{fig:nat_evaluation_result}, the throughput value show that the performances of large packets such as 1024 bytes and 1470 bytes is better than small packets. Because the NAT service need to set the packet header field and small payload size would send more packets to server at the same time, the performance of larger packets is well. We can see that the throughput value of multiple table framework is close to single table framework. So we can realize the multiple table framework is more flexible than single table framework, and the performance is close to each other.

@@

\begin{figure}[!t]
\centering
\includegraphics[width=4.0in]{./figures/classification_classifying}
\caption{Architecture of our application identification system in classifying phase}
\label{fig:classifcation_evaluation}
\end{figure}

>>>>

% \setlength{\columnsep}{10mm}
% \setlength{\textwidth}2.5180mm}
% \setlength{\textheight}{250mm}
% \addtolength{\oddsidemargin}{-9mm}
% \addtolength{\topmargin}{-25mm}

@@

% *** Do not adjust lengths that control margins, column widths2.5 etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

@@

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex,
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation results for the network.}
%\label{fig_sim}
%\end{figure}

@@

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command,
% and the \label for the overall figure must come after \caption.
% \hfil is used as a separator to get equal spacing.
% Watch out that the combined width 2.5f all the subfigures on a
% line do not exceed the text width 2.5r a line break will occur.
%
%\begin{figure*}[!t]
%\centering
%\subfloat[Case I]{\includegraphics[width=2.5.5in]{box}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5.5in]{box}%
%\label{fig_second_case}}
%\caption{Simulation results for the network.}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat[]), but instead will
%  reference/describe all of them (a), (b), etc., within the main caption.
% Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
% labels, the optional argument to \subfloat must be present. If a
% subcaption is not desired, just leave its contents blank,
% e.g., \subfloat[].

@@

\begin{figure}[!t]
\centering
\caption{Overview of network function}
\includegraphics[width=2.5in]{./figures/nfv_overview}
\label{fig:nfv_overview}
\end{figure}

@@

\begin{figure}[!t]
\centering
\includegraphics[width=2.5in]{./figures/deployment}
\caption{Service Deployment Model}
\label{fig:vcpe_deploy}
\end{figure}

@@

\begin{figure}[!t]
\centering
\includegraphics[width=2.5in]{./figures/vcpe_framework_overview}
\caption{Overview of vCPE framework}
\label{fig:vcpe_framework}
\end{figure}

@@

\subsubsection{QoS}
Quality of Service (QoS) are always used to control the traffic flows of a network
and prevent the traffic to exceed the network capacity and cause traffic congestion.
Therefore we implement the bandwidth 2.5anagement using meter
which is defined within OpenFlow protocol 1.3 to set the limitation of the bandwidth.2.5Beside achieving network functions virtualization with SDN technology,
we also make the network administrator manage and monitor a network more easily.
As a result, we can offer the user the best network quality in the limited network resource without traffic congestion.
In this paper, our QoS integrates with a flow classification engine
and offers the three ways of bandwidth 2.5anagement:
\begin{itemize}
\item For a specific host..
\item For a specific host.
\item For a specific application from a host or a domain.
\end{itemize}

\subsection{Application Identification}
Application identification is to identify each flow
as an application name to enable QoS management system to do bandwidth 2.5ontrol or distribution at application level.
A flow is defined by 5-tuple (source IP, source port, destination IP, destination port, and transport layer protocol).
Applications include desktop applications, native mobile applications, and web applications,
such as Facebook, Skype, YouTube, Instagram, Line and WeChat.
We use supervised machine learning and a method based on inspecting domain name service (DNS) responses to do flow classification.
After application identification system classifies a flow as an application name,
it sends the classification result to a server with database.
The server stores the classification result into database, and waits for query with 5-tuple from QoS management system.
The detail will be described in section \ref{sec:app_classification}.

@@

\begin{figure}[!t]
\centering
\includegraphics[width=2.5in]{./figures/multiple_table}
\caption{The flow table order of our vCPE service}
\label{fig:table-seq}
\end{figure}

@@

\subsection{NAT}
\begin{figure}[!t]
\centering
\includegraphics[width=2.5in]{./figures/nat_illustrate}
\caption{Illustration of NAT service}
\label{fig:nat_illustration}
\end{figure}
The NAT service could allow a lot of hosts to use one public IP address to connect the network.
In order to achieve this thing, SDN controller have to set the packet header filed.
Because the SDN switch would set the field, the first packet have to go to controller.
And controller would add the flow to SDN switch, after that the packet would not go to controller.
It can decrease the burdens of the controller.

@@

In order to gather per-session statistics information, 5-tuple rules are needed. This is why we don’t add rules  based on mac address.  The controller installs a pair of dummy rules for every connection, and then request the switch to get current flow statistics every second. In this way, we can get the real-time bandwidth 2.5tatistics of each connection by just subtracting the byte count from byte count of last second.

\section{Application Identifier method} \label{sec:app_classification}
In order to let QoS management system be able to control or distribute bandwidth 2.5t application level, we designed and implemented an application identification system (also called flow classification system) to judge each flow is established by what application. In other words, the system can classify each flow as an application name in real time, rather than a rough category or a transport layer protocol.
We use supervised machine learning (ML) and a method based on inspecting domain name service (DNS) responses to do flow classification. Except for DNS responses, the system only analyzes transport layer information of packets without inspecting their payload

@@

\begin{figure}[!t]
\centering
\includegraphics[width=2.5in]{./figures/classification_training}
\caption{Architecture of our application identification system in training phase}
\label{fig:classifcation_training}
\end{figure}

\begin{figure}[!t]
\centering
\includegraphics[width=2.5in]{./figures/classification_classifying}
\caption{Architecture of our application identification system in classifying phase}
\label{fig:classifcation_classifying}
\end{figure}

@@

\begin{figure}[!t]
\centering
\includegraphics[width=2.5in]{./figures/nat_evaluation}
\caption{Multiple Table Performance Evaluation Scenario}
\label{fig:nat_evaluation}
\end{figure}

\begin{figure}[!t]
\centering
\includegraphics[width=2.5in]{./figures/nat_evaluation_result}
\caption{Result of Multiple Table Performance Evaluation}
\label{fig:nat_evaluation_result}
\end{figure}

The single table framework implementation is easier than multiple table framework, but the multiple table framework is more flexible. To verify the efficacy of multiple table vCPE framework, this experiment use the NAT service to compare the throughput between single table vCPE and multiple table vCPE.
To begin with, an overview of the experiment environment illustrated in Fig. \ref{fig:nat_evaluation}.  In this experiment, the controller is Ryu SDN controller, and run on the Dell PowerEdge R630 Rack Server. The SDN switch employ Pica8 P-3290 switch. We used the tool that iPerf2.0 could generate the network traffic. The iPerf server would be set a public IP address. And iPerf client connect to the SDN switch that the controller would execute the NAT service on the single and multiple table vCPE framework.
We use the iPerf  to generate the UDP packets and send to server from client, and set the fixed value to bandwidth 2.5t 100Mbps. These experiments would use diffrent payload sizes to inspect their performances.
As shown in Fig. \ref{fig:nat_evaluation_result}, the throughput value show that the performances of large packets such as 1024 bytes and 1470 bytes is better than small packets. Because the NAT service need to set the packet header field and small payload size would send more packets to server at the same time, the performance of larger packets is well. We can see that the throughput value of multiple table framework is close to single table framework. So we can realize the multiple table framework is more flexible than single table framework, and the performance is close to each other.

@@

\begin{figure}[!t]
\centering
\includegraphics[width=2.5in]{./figures/classification_classifying}
\caption{Architecture of our application identification system in classifying phase}
\label{fig:classifcation_evaluation}
\end{figure}
